Supporting Information for\\ ``A weakly structured stem for human origins in Africa''

### 2022-03-11 supplement.tex

\begin{document}
\title{Supporting Information for\\
``A weakly structured stem for human origins in Africa''}
\author{Aaron P. Ragsdale, Timothy D. Weaver, Brenna M. Henn, and Simon Gravel}
\date{\today}
\maketitle

@@

Low coverage (4-8x) Illumina short read data were generated for the Nama,
Gumuz, Amhara and Oromo populations as part of the African Diversity Reference
Panel (Sanger / Wellcome Trust) \citep{Gurdasani2015-qy,Pagani2015-pz} and
approved through a secondary data analysis agreement for this project. Briefly,
raw reads were aligned to GRCH37 with BWAmem, duplicates
marked with Picard MarkDuplicates, reads were realigned around indels with GATK
RealignerTargetCreater/IndelRealigner followed by BQSR with dbSNP 137.
Contamination checks were performed requiring that FREEMIX $<0.05$;
contamination checks resulted in the elimination of 22 Nama samples. We note
that the high heterozygosity in these genomes both due to inherent genetic
diversity and admixture may have violated base assumptions for this
heterozygosity check. Genomes were then variant called with GATK3.2 Unified
Genotyper \citep{DePristo2011-up} using joint calling across 2,478 individuals within
the ADRP dataset with a minimum base quality of 17. Data were merged with 1000
Genomes Phase 3 \citep{1000_Genomes_Project_Consortium2015-zq} using the union
of sites identified with bcftools isec (-n+1) \citep{Danecek2021-kc} then refined
with Variant Recalibrator with a truth sensitivity threshold of 99.5\%. HapMap
III and dbSNP 138 served as known sites while 1000 Genomes Phase 1 Omni2.5 and
Phase 1 genomic SNP served as the training set. After VR, no batch effects were
observed along PC1 and PC2 for 1000 Genomes vs. ADRP. Phasing on the combined
dataset was performed via SHAPEIT2 \citep{Delaneau2013-aw} and utilized the duoHMM
option for duos and trios. We present new whole-genome data for 82 Nama individuals 
available under accession number EGAD00001006198.
\comment{This makes is sound like these weren't generated for this project.}
Among these 82 Nama samples, we down-sampled the individuals to minimize
close relatives and admixture, such that 44 Nama genomes were retained.
Second- and third-degrees relatives were inferred from reconstructed
pedigrees with Omni2.5 SNP array data.
Individuals with $>70\%$ estimated Khoe-San ancestry were retained for
analysis, after partitioning ancestry into $k=6$ clusters with \texttt{ADMIXTURE}
\citep{Alexander2009-sw} where alternative ancestries represent European, West
African, Near Eastern, and East African gene flow.

@@

We used principal component analysis (PCA) from \texttt{scikit-learn}
\citep{Pedregosa2011-ke} and \texttt{ADMIXTURE} version 1.3.0
\citep{Alexander2011-aq} to summarize genetic diversity among a broader set of
1000 Genomes and ADRP populations (Figure~\ref{fig:1} in the main text). Data
filtering was identical for both analyses. We retained biallelic SNPs with no
missing data and minor allele frequency greater that 5\%. We then thinned the
remaining sites to remove SNPs in high linkage disequilibrium with one another.
We used the \texttt{locate\_unlinked} function from \texttt{scikit-allel}
version 1.2.1 \citep{Miles2021-yq} to identify SNPs in low linkage
disequilibrium, using a threshold of $r^2=0.1$, a window size of 100 SNPs, and
a step size of 20 SNPs, removing the remaining SNPs. This process was iterated
five times for each chromosome, resulting in 327,656 roughly unlinked SNPs used
in the PCA and \texttt{ADMIXTURE} analyses.

@@

Because we were concerned that cSFS analyses may be affected by incorrect
inference of the ancestral allele \cite{Hernandez2007-mf}, we computed the cSFS
for all mutations, and for transitions and transversions separately
(Figures~\ref{fig:supp-csfs-single-origin}--\ref{fig:supp-csfs-merger-with-stem-migration}).
Comparisons of these observed cSFS with model
predictions are discussed in the model prediction section below.

@@

Based on the geographical locations of present-day populations, we tentatively
labeled ancestral branches using a parsimony in migration, referring to South,
East, and West African branches
(S/E/W AFR, Figures~\ref{fig:1},~\ref{fig:supp-possible-models}). We do not know the
geographical location of these ancestral populations (nor even if they
correspond to populations with a well-defined geographic range), and these
labels should be considered as tentative. However, we found it useful to name
branches in reference to where in Africa their descendants are found.
Parameters were converted to physical units
(years, effective population sizes, etc)
assuming a human generation time of 29 years.

@@

We performed an initial round of optimization including all six populations
with a family of models including single- and multiple-stem scenarios as
described in the previous section. We identified parameters that reached
consistent values across all models. These included the timings of recent or
non-central divergences and admixture events:
\begin{itemize}
    \item East/West African population split: 60ka
    \item East African/European split: 50ka
    \item Neanderthal introgression to Eurasian branch: 45ka
    \item Neanderthal/human split: 550ka
    \item Eurasian back-to-African migration: 12ka
\end{itemize}
When testing multiple variations of the more complex models, we kept these
values fixed (see Table~\ref{tab:fixed-params} for a complete list of all fixed
parameters). This reduced the potential for overfitting the more complex
models, while reducing the computational cost of optimization.

Our models also included recent events to account for known migrations,
admixtures, and growths and declines in effective population sizes. Many of
these parameters were fixed based on previous historical, genetic, or
anthropological research, namely
\begin{itemize}
    \item East African pastoralist to South African admixture: 2ka \cite{}
    \item European to South African admixture: 10 generations ago \cite{}
    \item Mende population expansion and Gumuz population decline: 5ka \cite{}
    \item South African population decline following colonial admixture: 9 generations ago \cite{}
\end{itemize}
\comment{This could be organized with a bit more structure. E.g. by region, or by timepoint} \sgcomment{order chronologically}
While the dates of these events were fixed, the sizes and proportions were
allowed to vary in the fits. The total number of parameters that were
ultimately inferred were 21-31, depending on the complexity
of the model.

@@

\texttt{moments-LD} uses a composite likelihood approach to simultaneously fit relative
pairwise diversity and LD statistics over a range of recombination distances.
Likelihoods were computed independently for pairwise diversity and each
recombination distance bin using a multivariate Guassian likelihood function as
described in Section \ref{sec:computing-stats}. These were multiplied across
bins and the single set of heterozygosity statistics following the approach
detailed in \citet{Ragsdale2019-nt}. For each model tested, we ran multiple
rounds of optimization, alternating between the \emph{optimize\_log\_fmin},
\emph{optimize\_log\_powell}, and \emph{optimize\_lbfgsb} methods to explore
parameter space and hone in on the best fit parameters. Initial guesses for
parameters were chosen from demographically plausible starting points and then
perturbed to explore space, using gradient descent (on the log of the
parameters). The best fits from these initial rounds of optimization were then
chosen as the starting points for optimization using the Powell and/or the
L-BFGS-B methods (as implemented in the SciPy optimization package
\cite{Virtanen2020-kr}). This process was repeated with alternating
optimization methods until the best fit parameter set converged consistently.

@@

\tdwcomment{I have tried to make the terminology about human, hominin, etc.
consistent and unambiguous. To do this, I have avoided using "modern" because 
"modern human" can mean "anatomically modern human" or \emph{Homo sapiens}, 
but mostly in the paper we use it to mean "contemporary" or "present-day". I 
think we should use "contemporary human" or "present-day human" when we mean 
the latter and just "human" when we mean the former. I have made these changes 
in the main text and supplement, preferentially using "contemporary" but 
leaving "present-day" when it was already there. However, I think it would be 
best if Simon made these changes in the equations in this section, so I don't mess 
something up.}

To evaluate the degree to which divergence among contemporary human populations is
inherited from divergence between early stem population, we computed $f_4$
statistics of the form
\begin{equation}
    f_4(\text{stem}_1, \text{stem}_2; \text{modern}_1, \text{modern}_2) = 
    \E[(p_{\text{stem}_1} - p_{\text{stem}_2} )(p_{\text{modern}_1} -p_{\text{modern}_2} )]
    \label{eq:f4}
\end{equation}
This statistic measures co-linearity of genetic drift between contemporary
populations $v= (p_{\text{modern}_1} -p_{\text{modern}_2} )$ and stem populations
$w= (p_{\text{stem}_1} -p_{\text{stem}_2} )$ (see
Figures~\ref{fig:supp-f4s-single-origin}--\ref{fig:supp-f4s-merger-with-stem-migration}
and \citet{Lipson2020-cq} for an overview of $f_4$ statistics).

To contrast these statistics to divergence across contemporary populations,
\begin{equation}
    f_2(\text{modern}_1, \text{modern}_2) =
    \E[(p_{\text{modern}_1} -p_{\text{modern}_2} )^2],
\end{equation}
we interpret the $f$-statistics as scalar products between vectors $v$ and $w$, i.e.,  
$f_2(\text{modern}_1, \text{modern}_2) = v\cdot v$ and 
$f_4(\text{stem}_1, \text{stem}_2; \text{modern}_1, \text{modern}_2) = v\cdot w.$
We can then write $v=v_\perp + v_\parallel$ as the sum of a component $v_\perp$ perpendicular and
a component $v_\parallel$ parallel to $w = (p_{\text{stem}_1} -p_{\text{stem}_2} ).$
We can then decompose 
$f_2(\text{modern}_1,\text{modern}_2) = v_\perp^2+v_\parallel^2$, with  
\begin{equation}
    v_\parallel^2 = \frac{(v \cdot w)^2}{w\cdot w} = \frac{ f_4^2(\text{stem}_1, \text{stem}_2; 
    \text{modern}_1, \text{modern}_2)}{f_2(\text{stem}_1, \text{stem}_2)}
\end{equation}

Finally, the proportion of present-day structure
$v^2 = f_2(\text{modern}_1, \text{modern}_2)$ that is accounted for by the
component parallel to ancient population structure is
\begin{equation}
    \alpha^2 = \frac{v_\parallel^2}{v^2} =
    \frac{f_4^2(\text{stem}_1, \text{stem}_2; \text{modern}_1, \text{modern}_2)}
    {f_2(\text{stem}_1,\text{stem}_2)f_2(\text{modern}_1, \text{modern}_2)}.
\end{equation}
$\alpha^2$ can be interpreted as the proportion of the $f_2$
divergence across contemporary populations that is aligned with the differences in
allele frequencies across ancient populations. However, drift occurring after
the time of sampling of ancient populations is not correlated to drift
occurring before that time. For this reason, we also interpret $\alpha^2$ as the
proportion of the $f_2$ divergence across contemporary populations that is \emph{explained by}
the differences in allele frequencies across ancient populations. We report
this predicted statistic for each of the four inferred demographic models in
Figures~\ref{fig:supp-f4s-single-origin}--\ref{fig:supp-f4s-merger-with-stem-migration}.

\begin{figure}[ht]
    \centering
    \includegraphics[width=0.75\textwidth]{figures/supp-f4-scenarios}
    \caption{
        \textbf{Present-day structure attributable to ancient population structure.}
        The statistic 
        $f_4(\text{stem}_1, \text{stem}_2; \text{modern}_1, \text{modern}_2)$
        captures how much of present-day population structure can be attributed to 
        population structure among the stems. The blue line represents genetic drift 
        along ancestral branches between contemporary populations, while the red line 
        represents drift between stem populations. $f_4$ measures the overlap 
        between the blue and red line, which corresponds to shared genetic drift 
        between the two pairs. 
        In scenario A, contemporary populations are descended from distinct stems, and 
        $f_4(\text{stem}_1, \text{stem}_2; \text{modern}_1, \text{modern}_2)$
        equals the drift between stems, $f_2(\text{stem}_1, \text{stem}_2)$.
        In scenario B, despite deep population structure, there is no shared drift
        and $f_4=0$. That is, present-day population structure is unrelated to
        structure among stems. In more realistic scenario C, where $\text{modern}_1$
        receives a proportion $m$ of its ancestry from the dotted arrow, the overlap
        is only found along the corresponding path, and $f_4$ depends on both
        ancestry proportion $m$ and drift between stems,
        $f_4(\text{stem}_1, \text{stem}_2; \text{modern}_1, \text{modern}_2)
        = mf_2(\text{stem}_1, \text{stem}_2)$
    }
    \label{fig:supp-f4-scenarios}
\end{figure}

@@

\begin{figure}[ht]
    \centering
    \includegraphics[width=0.65\textwidth]{figures/supp-possible-models.png}
    \caption{
        \textbf{Models of early human history in Africa} seeking to reconcile genetic and paleoanthropological evidence \cite{Henn2018-rf}.
         \comment{Lovely figure, may even want to move to main text}
    }
    \label{fig:supp-possible-models}
\end{figure}

>>>>

\begin{document}
\title{Supporting Information for\\
``A weakly structured stem for human origins in Africa''}
\author{Aaron P. Ragsdale, Timothy D. Weaver, Elizabeth G. Atkinson, Eileen Hoal, Marlo M\"{o}ller, Brenna M. Henn, and Simon Gravel}
\date{\today}
\maketitle

@@

Low coverage (4-8x) Illumina short read data were generated for the Nama,
Gumuz, Amhara and Oromo populations as part of the African Diversity Reference
Panel (Sanger / Wellcome Trust) \citep{Gurdasani2015-qy,Pagani2015-pz} and
approved through a secondary data analysis agreement for this project. Briefly,
raw reads were aligned to GRCH37 with BWAmem, duplicates
marked with Picard MarkDuplicates, reads were realigned around indels with GATK
RealignerTargetCreater/IndelRealigner followed by BQSR with dbSNP 137.
Contamination checks were performed requiring that FREEMIX $<0.05$;
contamination checks resulted in the elimination of 22 Nama samples. We note
that the high heterozygosity in these genomes both due to inherent genetic
diversity and admixture may have violated base assumptions for this
heterozygosity check. Genomes were then variant called with GATK3.2 Unified
Genotyper \citep{DePristo2011-up} using joint calling across 2,478 individuals within
the ADRP dataset with a minimum base quality of 17. Data were merged with 1000
Genomes Phase 3 \citep{1000_Genomes_Project_Consortium2015-zq} using the union
of sites identified with bcftools isec (-n+1) \citep{Danecek2021-kc} then refined
with Variant Recalibrator with a truth sensitivity threshold of 99.5\%. HapMap
III and dbSNP 138 served as known sites while 1000 Genomes Phase 1 Omni2.5 and
Phase 1 genomic SNP served as the training set. After VR, no batch effects were
observed along PC1 and PC2 for 1000 Genomes vs. ADRP. Phasing on the combined
dataset was performed via SHAPEIT2 \citep{Delaneau2013-aw} and utilized the duoHMM
option for duos and trios. We present new whole-genome data for 82 Nama individuals 
available under accession number EGAD00001006198.
Among these 82 Nama samples, we down-sampled the individuals to minimize
close relatives and admixture, such that 44 Nama genomes were retained.
Second- and third-degrees relatives were inferred from reconstructed
pedigrees with Omni2.5 SNP array data.
Individuals with $>70\%$ estimated Khoe-San ancestry were retained for
analysis, after partitioning ancestry into $k=6$ clusters with \texttt{ADMIXTURE}
\citep{Alexander2009-sw} where alternative ancestries represent European, West
African, Near Eastern, and East African gene flow.

@@

We used principal component analysis (PCA) from \texttt{scikit-learn}
\citep{Pedregosa2011-ke} and \texttt{ADMIXTURE} version 1.3.0
\citep{Alexander2011-aq} to summarize genetic diversity among a broader set of
1000 Genomes and ADRP populations (Figure~\ref{fig:diversity} in the main text). Data
filtering was identical for both analyses. We retained biallelic SNPs with no
missing data and minor allele frequency greater that 5\%. We then thinned the
remaining sites to remove SNPs in high linkage disequilibrium with one another.
We used the \texttt{locate\_unlinked} function from \texttt{scikit-allel}
version 1.2.1 \citep{Miles2021-yq} to identify SNPs in low linkage
disequilibrium, using a threshold of $r^2=0.1$, a window size of 100 SNPs, and
a step size of 20 SNPs, removing the remaining SNPs. This process was iterated
five times for each chromosome, resulting in 327,656 roughly unlinked SNPs used
in the PCA and \texttt{ADMIXTURE} analyses.

@@

Because we were concerned that cSFS analyses may be affected by incorrect
inference of the ancestral allele \citep{Hernandez2007-mf}, we computed the cSFS
for all mutations, and for transitions and transversions separately
(Figures~\ref{fig:supp-csfs-single-origin}--\ref{fig:supp-csfs-merger-with-stem-migration}).
Comparisons of these observed cSFS with model
predictions are discussed in the model prediction section below.

@@

Based on the geographical locations of present-day populations, we tentatively
labeled ancestral branches using a parsimony in migration, referring to South,
East, and West African branches
(S/E/W AFR, Figures~\ref{fig:proposed-models},~\ref{fig:diversity}). We do not know the
geographical location of these ancestral populations (nor even if they
correspond to populations with a well-defined geographic range), and these
labels should be considered as tentative. However, we found it useful to name
branches in reference to where in Africa their descendants are found.
Parameters were converted to physical units
(years, effective population sizes, etc)
assuming a human generation time of 29 years.

@@

We performed an initial round of optimization including all six populations
with a family of models including single- and multiple-stem scenarios as
described in the previous section. We identified parameters that reached
consistent values across all models. These included the timings of recent or
non-central divergences and admixture events:
\begin{itemize}
    \item Neanderthal/human split: 550ka
    \item East/West African population split: 60ka
    \item East African/European split: 50ka
    \item Neanderthal introgression to Eurasian branch: 45ka
    \item Eurasian back-to-African migration: 12ka
\end{itemize}
When testing multiple variations of the more complex models, we kept these
values fixed (see Table~\ref{tab:fixed-params} for a complete list of all fixed
parameters). This reduced the potential for overfitting the more complex
models, while reducing the computational cost of optimization.

Our models also included recent events to account for known migrations,
admixtures, and growths and declines in effective population sizes. Many of
these parameters were fixed based on previous historical, genetic, or
anthropological research, namely
\begin{itemize}
    \item Mende population expansion and Gumuz population decline: 5ka \citep{Gopalan2022-pw}
    \item East African pastoralist to South African admixture: 2ka \citep{Uren2016-nn}
    \item European to South African admixture: 10 generations ago
    \item South African population decline following colonial admixture: 9 generations ago
\end{itemize}
allowed to vary in the fits. The total number of parameters that were
ultimately inferred were 21-31, depending on the complexity
of the model.

@@

\texttt{moments-LD} uses a composite likelihood approach to simultaneously fit relative
pairwise diversity and LD statistics over a range of recombination distances.
Likelihoods were computed independently for pairwise diversity and each
recombination distance bin using a multivariate Guassian likelihood function as
described in Section \ref{sec:computing-stats}. These were multiplied across
bins and the single set of heterozygosity statistics following the approach
detailed in \citet{Ragsdale2019-nt}. For each model tested, we ran multiple
rounds of optimization, alternating between the \emph{optimize\_log\_fmin},
\emph{optimize\_log\_powell}, and \emph{optimize\_lbfgsb} methods to explore
parameter space and hone in on the best fit parameters. Initial guesses for
parameters were chosen from demographically plausible starting points and then
perturbed to explore space, using gradient descent (on the log of the
parameters). The best fits from these initial rounds of optimization were then
chosen as the starting points for optimization using the Powell and/or the
L-BFGS-B methods (as implemented in the SciPy optimization package
\citep{Virtanen2020-kr}). This process was repeated with alternating
optimization methods until the best fit parameter set converged consistently.

@@

%\tdwcomment{I have tried to make the terminology about human, hominin, etc.
%consistent and unambiguous. To do this, I have avoided using "modern" because 
%"modern human" can mean "anatomically modern human" or \emph{Homo sapiens}, 
%but mostly in the paper we use it to mean "contemporary" or "present-day". I 
%think we should use "contemporary human" or "present-day human" when we mean 
%the latter and just "human" when we mean the former. I have made these changes 
%in the main text and supplement, preferentially using "contemporary" but 
%leaving "present-day" when it was already there. However, I think it would be 
%best if Simon made these changes in the equations in this section, so I don't mess 
%something up.}

To evaluate the degree to which divergence among contemporary human populations is
inherited from divergence between early stem population, we computed $f_4$
statistics of the form
\begin{equation}
    f_4(\text{stem}_1, \text{stem}_2; \text{modern}_1, \text{modern}_2) = 
    \E[(p_{\text{stem}_1} - p_{\text{stem}_2} )(p_{\text{present}_1} -p_{\text{present}_2} )]
    \label{eq:f4}
\end{equation}
This statistic measures co-linearity of genetic drift between contemporary
populations $v= (p_{\text{present}_1} -p_{\text{present}_2} )$ and stem populations
$w= (p_{\text{stem}_1} -p_{\text{stem}_2} )$ (see
Figures~\ref{fig:supp-f4s-single-origin}--\ref{fig:supp-f4s-merger-with-stem-migration}
and \citet{Lipson2020-cq} for an overview of $f_4$ statistics).

To contrast these statistics to divergence across contemporary populations,
\begin{equation}
    f_2(\text{present}_1, \text{present}_2) =
    \E[(p_{\text{present}_1} -p_{\text{present}_2} )^2],
\end{equation}
we interpret the $f$-statistics as scalar products between vectors $v$ and $w$, i.e.,  
$f_2(\text{present}_1, \text{present}_2) = v\cdot v$ and 
$f_4(\text{stem}_1, \text{stem}_2; \text{present}_1, \text{present}_2) = v\cdot w.$
We can then write $v=v_\perp + v_\parallel$ as the sum of
a component $v_\perp$ perpendicular and
a component $v_\parallel$ parallel to
$w = (p_{\text{stem}_1} -p_{\text{stem}_2} ).$
We can then decompose 
$f_2(\text{present}_1,\text{present}_2) = v_\perp^2+v_\parallel^2$, with  
\begin{equation}
    v_\parallel^2 = \frac{(v \cdot w)^2}{w\cdot w} = \frac{ f_4^2(\text{stem}_1, \text{stem}_2; 
    \text{present}_1, \text{present}_2)}{f_2(\text{stem}_1, \text{stem}_2)}
\end{equation}

Finally, the proportion of present-day structure
$v^2 = f_2(\text{present}_1, \text{present}_2)$ that is accounted for by the
component parallel to ancient population structure is
\begin{equation}
    \alpha^2 = \frac{v_\parallel^2}{v^2} =
    \frac{f_4^2(\text{stem}_1, \text{stem}_2; \text{present}_1, \text{present}_2)}
    {f_2(\text{stem}_1,\text{stem}_2)f_2(\text{present}_1, \text{present}_2)}.
\end{equation}
$\alpha^2$ can be interpreted as the proportion of the $f_2$
divergence across contemporary populations that is aligned with the differences in
allele frequencies across ancient populations. However, drift occurring after
the time of sampling of ancient populations is not correlated to drift
occurring before that time. For this reason, we also interpret $\alpha^2$ as the
proportion of the $f_2$ divergence across contemporary populations that is
\emph{explained by} the differences in allele frequencies across ancient populations.
We report this predicted statistic for each of the four inferred demographic models in
Figures~\ref{fig:supp-f4s-single-origin}--\ref{fig:supp-f4s-merger-with-stem-migration}.
In our best fit models (continuous migration and merger with stem migration),
differentiation between Stem 1 and Stem 2
(before the split of Stem 1 into Stem 1E and Stem 1S in the merger model)
contributes a maximum of $4\%$ to differentiation between the Nama and Gumuz, and closer
to $1\%$ to differentiation between the Nama and Mende or the Mende and Gumuz.

\begin{figure}[ht]
    \centering
    \includegraphics[width=0.75\textwidth]{figures/supp-f4-scenarios}
    \caption{
        \textbf{Present-day structure attributable to ancient population structure.}
        The statistic 
        $f_4(\text{stem}_1, \text{stem}_2; \text{present}_1, \text{present}_2)$
        captures how much of present-day population structure can be attributed to 
        population structure among the stems. The blue line represents genetic drift 
        along ancestral branches between contemporary populations, while the red line 
        represents drift between stem populations. $f_4$ measures the overlap 
        between the blue and red line, which corresponds to shared genetic drift 
        between the two pairs. 
        In scenario A, contemporary populations are descended from distinct stems, and 
        $f_4(\text{stem}_1, \text{stem}_2; \text{present}_1, \text{present}_2)$
        equals the drift between stems, $f_2(\text{stem}_1, \text{stem}_2)$.
        In scenario B, despite deep population structure, there is no shared drift
        and $f_4=0$. That is, present-day population structure is unrelated to
        structure among stems. In more realistic scenario C, where $\text{present}_1$
        receives a proportion $m$ of its ancestry from the dotted arrow, the overlap
        is only found along the corresponding path, and $f_4$ depends on both
        ancestry proportion $m$ and drift between stems,
        $f_4(\text{stem}_1, \text{stem}_2; \text{present}_1, \text{present}_2)
        = mf_2(\text{stem}_1, \text{stem}_2)$
    }
    \label{fig:supp-f4-scenarios}
\end{figure}

@@
